---
title: "p8105_hw6_jf3286.Rmd"
author: "Jingyu Fu"
date: "2019/11/19"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```



# Problem 1
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
data1 = read_csv(file = "./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
   babysex = as.character(babysex),
    babysex = fct_infreq(babysex),
   frace = as.character(frace),
    frace = fct_infreq(frace),
    malform = as.character(malform),
    malform = fct_infreq(malform),
   mrace = as.character(mrace),
    mrace = fct_infreq(mrace)
  )

data1 %>% is.na()
  
data1 = data1 %>% drop_na()



```


Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
#regression model
pro_mod = lm(bwt ~ babysex + bhead + blength, data = data1)


#plot

data11 = data1 %>% 
  modelr::add_residuals(pro_mod) %>% 
   add_predictions(pro_mod) 
   
data11 %>% 
    ggplot(aes(x = pred, y = resid)) + geom_point()

```
description: according to the common aknowledge about factors that may effect birthweight, the most closely relevant factors would be baby's sex, head cricumference, and length at birth. 



Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
mod1 = data1 %>% 
lm(bwt ~ blength + gaweeks, data = .)
  
mod2 = data1 %>% 
    lm(bwt ~ bhead*babysex + blength*babysex + babysex, data = .)

```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
```{r}
cv_df1 =
  crossv_mc(data1, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))


cv_df11 = 
  cv_df1 %>% 
  mutate(pro_mod  = map(train, ~lm(bwt ~ babysex + bhead + blength, data = data1)),
         mod1  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         mod2  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_pro = map2_dbl(pro_mod, test, ~rmse(model = .x, data = .y)),
         rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y)))
```


# Problem 2

load in the data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```
