---
title: "p8105_hw6_jf3286.Rmd"
author: "Jingyu Fu"
date: "2019/11/19"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```



# Problem 1

Load and clean the data for regression analysis. I converted numeric to factor, checked for missing data.

```{r}
data1 = read_csv(file = "./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
   babysex = as.character(babysex),
    babysex = fct_infreq(babysex),
   frace = as.character(frace),
    frace = fct_infreq(frace),
    malform = as.character(malform),
    malform = fct_infreq(malform),
   mrace = as.character(mrace),
    mrace = fct_infreq(mrace)
  )

data1 %>% is.na()
  
data1 = data1 %>% drop_na()



```


Propose a regression model for birthweight. 

```{r}
pro_mod = lm(bwt ~ babysex + bhead + blength, data = data1)
```

Making a plot.

```{r}
data11 = data1 %>% 
  modelr::add_residuals(pro_mod) %>% 
   add_predictions(pro_mod) 
   
data11 %>% 
    ggplot(aes(x = pred, y = resid)) + geom_point()

```
Description: according to the common aknowledge about factors that may effect birthweight, the most closely relevant factors would be baby's sex, head cricumference, and length at birth. 



Compare my model to two others:

```{r}
cv_df1 =
  crossv_mc(data1, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))


cv_df11 = 
  cv_df1 %>% 
  mutate(pro_mod  = map(train, ~lm(bwt ~ babysex + bhead + blength, data = .x)),
         mod1  = map(train, ~lm(bwt ~ babysex + blength, data = .x)),
         mod2  = map(train, ~lm(bwt ~ babysex * bhead * blength, data = .x))) %>% 
  mutate(rmse_pro = map2_dbl(pro_mod, test, ~rmse(model = .x, data = .y)),
         rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y)))

cv_df11 %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
Comparison: From the violin plot of rmse vs model, we can tell that model 2 is the best model (bwt ~ babysex * bhead * blength), the one using head circumference, length, sex, and all interactions (including the three-way interaction) between these.


# Problem 2

Load in the data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```
Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two 
quantities.

```{r}
weather1 = weather_df %>% 
  modelr::bootstrap(n = 10) 


weather11 = weather1 %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
select(-strap, -models) %>% 
  unnest(results) %>% 
  select(.id, r.squared) %>% 
  janitor::clean_names()


weather12 = weather1 %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy))  
select(-strap, -models) %>% 
  unnest(results) %>% 
  select(.id,term,estimate) %>% 
  group_by(.id) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  janitor::clean_names() %>% 
  ungroup()
  
weather121 = weather12 %>% 
  group_by(id) %>% 
mutate(
    logb = log(intercept * tmin)
  )
  
```



Plot the distribution of my estimates, and describe these in words. 
```{r}
weather11 %>% 
ggplot(aes(x = id, y = r_squared)) + 
  geom_point(alpha = .5)


weather121 %>% 
  ggplot(aes(x = id, y = logb)) + 
  geom_point(alpha = .5)
```
Description: 


Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r^2. 

```{r}
quantile(pull(weather11, r_squared),c(.025,.975))
```
Therefore, the 95% confidence interval for r^2 is (0.9006987, 0.9185960).


Identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for log(β^0∗β^1). 
```{r}
quantile(pull(weather121, logb),c(.025,.975))
```
Therefore, the 95% confidence interval for log(β^0∗β^1) is (1.976589, 2.062677).

